Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-04-20 Paper/Manuscript.tex
Updated Figure 11

Target strength can then be estimated using Eq. \ref{eq:TS}:
\begin{equation}
\label{eq:TS_f}
\ts(\freqsym) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\freqsym)\range_t - 10\log_{10}\left( \frac{\ptxe \wlen^2 \gain^2(\along_t,\athw_t,f)}{16\pi^2} \right)
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The discrete fourier transform of the target signal $\ypctargetf(\samplesymf)$ (a) and the reduced auto correlation signal $\ymfautoredf(\samplesymf)$ (b). The normalized discrete Fourier transform of the target signal $\ypctargetnormf(\samplesymf)$ (c) and finally the estimated TS(f) (d).}
\end{figure}

@@

As a metallic sphere is a rather simple and ideal scatterer, we use $\sv$ from a school of non-swimbladdered fish (\textit{tobis}) (fig.~\ref{Fig_Sv_echogram}) collected with a 120 kHz centre frequency transducer to illustrate the processes to obtain $S_v(m)$.

>>>>

Target strength can then be estimated using Eq. \ref{eq:TS}:
\begin{equation}
\label{eq:TS_f}
\ts(\freqsym) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\freqsym)\range_t - 10\log_{10}\left( \frac{\ptxe \wlen^2 \gain^2(\along_t,\athw_t,f)}{16\pi^2} \right)
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The discrete Fourier transform of the target signal $\ypctargetf(\samplesymf)$ (a) and the reduced auto correlation signal $\ymfautoredf(\samplesymf)$ (b), the normalized discrete Fourier transform of the target signal $\ypctargetnormf(\samplesymf)$ (c) and the estimated TS(f) (d).}
\end{figure}

@@

As a metallic sphere is a rather simple and ideal scatterer, we use $\sv$ from a school of non-swimbladdered fish (fig.~\ref{Fig_Sv_echogram}) collected with a 120 kHz centre frequency transducer to illustrate the processes to obtain $S_v(m)$.
